Analysis PPM-S

### 2020-06-10 production/prod_analysis-cfa.rmd

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("A. pc.effort", "B. pc.talent","C. pc.wpart","D. pc.netw","E. pf.effort","F. pf.talent","G. pf.wpart", "H. pf.netw")
colnames(cor04$rho) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

# Anexo 1: Sample

>>>>

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("A.Perception Effort", "B.Perception Talent","C.Perception Rich parents","D.Perception contacts","E.Preferences Effort","F.Preferences Talent","G.Preferences rich parents", "H.Preferences contacts" )
colnames(cor04$rho) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
save(cor04, file = "output/images/correlation.RData")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)

png("output/images/corpoly.png",
    width = 15,height = 15,units="cm",
    pointsize=12,bg="white",res=300)

corrplot(cor01$rho,method = "color" ,type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)

dev.off()
```

@@

```{r}
library(ggplot2)
library(reshape2)
library(sjPlot)
library(dplyr)

#install.packages("cowplot")
library(cowplot)

dat_merit <- dat04 %>% select("a.Effort"=perc_effort,"a.Talent"=perc_talent, "a.Rich Parents"=perc_wpart, "a.Contacts"=perc_netw, "b.Effort"=pref_effort,"b.Talent"=pref_talent,"b.Rich Parents"=pref_wpart, "b.Contacts"=pref_netw)

plotlikert<-plot_likert(dat_merit, c(1,1,1,1,2,2,2,2),
            groups.titles = c("Perceptions","Preferences"),
            geom.colors ="PuBu", 
            geom.size = 0.8,
            axis.labels=c("Effort","Talent","Rich Parents","Contacts"),
            catcount = 4,
            cat.neutral = 3, 
            grid.range  =  c ( 1.2 , 1.4 ),
            values  =  "sum.outside",
            reverse.scale=TRUE)
plotlikert

ggsave(plotlikert,filename = "output/images/plotlikert.png",device = "png",width = 18,height = 15,dpi = "retina",units = "cm")

=======
# Anexo 1: Sample
